### 2016-07-07 lineups.Rnw
added figure 7 output back in

@
\caption{\label{fig:lusparms} Scatterplots of smallfriends and smallfriends-rev: comparing the ratio of null plots with smaller estimates of $\beta_3$ in the nulls than in the data panel (top row) and larger estimates of $\beta_3$ in the nulls than in the data panel. In lineups with a ratio of 1 the data should be 'easy' to identify in both scenarios.}
\end{figure}

>>>>

p2 <- qplot(data_dist, lower_qu, data = subset(lus_summary_2b, part %in% c("smallfriends", "smallfriends-rev") & param_name=="transitive triplets jumping alcohol2")) +
  facet_grid(.~part) + xlab("Difference in M2 estimate of data panel and minimum of the null panels") +
  ylab("Ratio of null panels with larger M2 estimate") +
  ggtitle("jumping transitive triplets")

gridExtra::grid.arrange(p1,p2)
@
\caption{\label{fig:lusparms} Scatterplots of smallfriends and smallfriends-rev: comparing the ratio of null plots with smaller estimates of $\beta_3$ in the nulls than in the data panel (top row) and larger estimates of $\beta_3$ in the nulls than in the data panel. In lineups with a ratio of 1 the data should be 'easy' to identify in both scenarios.}
\end{figure}
